The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-09-21 paper/draft.tex
lay out abstract

\begin{abstract}

@@

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species.

>>>>

\begin{abstract}
  Islands feature peculiar and fascinating biotas, often very distinct from any other island or continental area.
  [Examples of radiations/good and poor radiators, island syndromes etc.]
  Although island biogeography theory has seen an ever increasing development over the years,
  the mechanisms underlying these patterns are not fully understood/ not yet explained in a direct causal relationship.
  Specifically, some processes remain un- or under-explored, foremost of these adaption and micro-evolution.
  We used an individual-based mechanistic model implementing these processes and other commonly investigated ecological and
  environmental processes to assess the importance of drivers across different organisational and spatio-temporal levels
  on species trait distribution on islands.
  This enabled us to also take a closer look on the properties of lineages/species that actually managed to colonize islands,
  and which of them resulted in radiations[~].

@@

Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
island colonisation, while others remain one single species (Price/Chase).
